%% Based on a TeXnicCenter-Template by Gyorgy SZEIDL.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{article}%%
\renewcommand{\baselinestretch}{1}

\usepackage{amsmath}%
\usepackage{hyphenat}%
\usepackage{amsfonts}%
\usepackage{amssymb}%
\usepackage{graphicx}
\usepackage{lipsum}
\usepackage{ragged2e}
\usepackage{bm}
\usepackage[margin = 20 mm]{geometry}
\usepackage{graphicx}
\usepackage{wrapfig}
 \geometry{
 a4paper,
 total={210mm,297mm},
 left=20mm,
 right=20mm,
 top=20mm,
 bottom=10mm,
 }
\usepackage{enumerate}
\usepackage{hyperref}
\RequirePackage[fixed]{fontawesome5}

\pagenumbering{gobble}
\begin{document}
\begin{flushleft}
\textbf{\Large{\huge Aarish Alam}}
\end{flushleft}
{\textbf{\href{mailto:arishalam121@gmail.com}{arishalam121@gmail.com}}}
\hfill{Mobile No. \textbf{7223015989}}

\begin{flushleft}
{\href{https://behavior.systems/}{\textbf{Portfolio Website}}}\hfill
\begin{minipage}{0.4\textwidth}
\raggedleft
\href{https://github.com/RheagalFire}{\faGithub}\hspace{2mm}
\href{https://www.linkedin.com/in/aarish-alam/}{\faLinkedin}\hspace{2mm}
\href{https://arishalam121.medium.com/}{\faMedium}\hspace{2mm}
\href{https://www.kaggle.com/arishalam}{\faKaggle}
\end{minipage}
\end{flushleft}

%===========================
\vspace{2mm}
\begin{flushleft}
\bf{\Large{Work Experience}}
\end{flushleft}
\vspace{-2mm}
\noindent\rule{\textwidth}{0.4pt}
\vspace{2mm}
Founding AI \& Platform Engineer, \textbf{Scaled Focus} \hfill{April 2025 - Present}
\vspace{-1mm}
\begin{itemize}
\setlength\itemsep{0.01em}
\item \textbf{Littlebird -- AI Evaluation Systems}: Designed and built evaluation frameworks for AI agents, enabling systematic measurement of agent performance across production workflows.
\item \textbf{Kavana -- Observability \& Evals}: Setup \textbf{Langfuse} observability infrastructure on \textbf{EKS (Elastic Kubernetes Service)} handling \textbf{1M+ ingestions/day}, building end-to-end tracing and evaluation pipelines for LLM-powered products.
\item \textbf{Kavana -- Cost \& Engagement Optimization}: Implemented \textbf{explicit caching} reducing costs by \textbf{75\%} and \textbf{rolling summarization} improving engagement by \textbf{20\%} while decreasing costs by \textbf{20\%}.
\end{itemize}
\vspace{-1mm}
OSS Maintainer, \textbf{LiteLLM} (W23) \hfill{2026 - Present}
\vspace{-1mm}
\begin{itemize}
\setlength\itemsep{0.01em}
\item Contributing to \textbf{LiteLLM} as an open-source maintainer, building and maintaining the unified API gateway that provides a standardized interface across \textbf{100+ LLM providers}.
\item Reviewing PRs, triaging issues, and implementing features for the proxy server and SDK used in thousands of production deployments.
\end{itemize}
\vspace{-1mm}
AI Engineer, \textbf {FutureOps} \hfill{March 2024 - April 2025}
\vspace{-1mm}
\begin{itemize}
\setlength\itemsep{0.01em}
\item \textbf{Chat and Voice Systems}: Built chat and voice systems using agentic workflows, \textbf{Hybrid RAG}, and \textbf{RRF}, achieving over \textbf{85\% precision and context recall}. Developed an agentic querying system for Kubernetes pods and databases using \textbf{LangGraph} and \textbf{MCP servers}.
\item \textbf{LLM Observability \& Guardrails}: Built an end-to-end evaluation suite using \textbf{RAGAS} and observability pipeline with \textbf{Phoenix} (OpenTelemetry). Implemented \textbf{Guardrails AI} and PII detection for data security.
\end{itemize}
\vspace{-1mm}
ML Engineer, \textbf {Fold Money} \hfill{July 2023 - March 2024}
\vspace{-1mm}
\begin{itemize}
\setlength\itemsep{0.01em}
\item \textbf{Fine-Tuning DistilBERT for Transaction Categorization}: Fine-tuned a \textbf{DistilBERT} model to identify transaction categories, achieving \textbf{precision of 97\% and recall of 90\%}. Built a smart search model using \textbf{RASA} and semantic search over a vector database.
\item \textbf{Hybrid Tagging System}: Developed a hybrid tagging system combining rule-based and ML approaches that adapted to user behavior.
    \hfill \href{https://fold.money/blog/automating-transaction-tagging}{\faGlobe}
\end{itemize}
\vspace{-1mm}
SWE Intern, \textbf {Phonepe} \hfill{Jan 2023 - Jun 2023}
\vspace{-1mm}
\begin{itemize}
\setlength\itemsep{0.01em}
\item \textbf{ETL Pipeline for Agent Training Data}: Engineered an ETL pipeline to process agent training documents and performance metrics. Utilized \textbf{Looker Studio} to create dynamic dashboards for real-time monitoring.
    \item \textbf{Support Workflow Optimization}: Applied \textbf{K-means Clustering} and \textbf{Jina-Embeddings-v3} to analyze and cluster multilingual support tickets, identifying patterns and optimal solutions.
\end{itemize}
\vspace{-1mm}
Data Science Intern, \textbf{Shopagain} \hfill{Dec 2021 - Dec 2022}
\vspace{-1mm}
\begin{itemize}
\setlength\itemsep{0.01em}
\item \textbf{Customer Lifetime Value Prediction}: Developed modules to predict the lifetime value of the customer based on browsing, purchase and demographic data.
    \item \textbf{Real-Time Intent Prediction}: Built and deployed a real-time prediction module for the intent of the customer to purchase products from session data, with comprehensive monitoring systems.
\end{itemize}

\pagebreak

%===========================
\begin{flushleft}
\bf{\Large{Projects}}
\end{flushleft}
\vspace{-2mm}
\noindent\rule{\textwidth}{0.4pt}
\vspace{2mm}

\begin{itemize}
\setlength\itemsep{2mm} % slight vertical gap between items

% Project 1
\item
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
\textbf{LLM-Gym} &
\href{https://github.com/RheagalFire/LLM-gym/tree/main/gym_reader}{\faGithub} \hspace{2mm}
\href{https://www.linkedin.com/posts/aarish-alam_rag-dspy-knowledgemanagement-activity-7288050529685975042-uNUi?utm_source=share&utm_medium=member_desktop&rcm=ACoAAC3guzgBLJ3ujDvj7NqMMjTw1_2SwpYn4dE}{\faLinkedin}
\end{tabular*} \\
\justifying
Built a semantic search and chat tool to retrieve bookmarked articles using \textbf{Qdrant} and \textbf{Meilisearch}, enabling hybrid search over both summaries and full content. Used \textbf{DSPy} with \textbf{Instructor} for prompt tuning and validation. Integrated CI/CD workflows via \textbf{GitHub Actions} and deployed the infrastructure on AWS using \textbf{Terraform}.

% Project 2
\item
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
\textbf{Browser-side Inferencing} &
\href{https://github.com/RheagalFire/Browserside-Inferencing}{\faGithub}
\end{tabular*} \\
\justifying
Implemented fast and efficient model execution using \textbf{ONNX Runtime} and deployed the models with \textbf{WebAssembly}, ensuring seamless cross-platform compatibility.

% Project 3
\item
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
\textbf{Personalized Chat Bot} &
\href{https://github.com/RheagalFire/personalized_chat_bot}{\faGithub}
\end{tabular*} \\
\justifying
Built a personalized chatbot using \textbf{LangChain} for structured dialogue and \textbf{Pinecone} for vector storage, enabling semantic search and user-specific retrieval across conversations.

\end{itemize}



%===========================
\begin{flushleft}
\bf{\Large{Talks}}
\end{flushleft}
\vspace{-1mm}
\noindent\rule{\textwidth}{0.4pt}
\begin{itemize}
\item Speaker at PyData Bangalore on Scalable Hybrid RAG\hfill
\href{https://www.linkedin.com/posts/pydata-bangalore_pydata-bangalore-machinelearning-activity-7298222664903495680-XK4G?utm_source=share&utm_medium=member_desktop&rcm=ACoAAC3guzgBLJ3ujDvj7NqMMjTw1_2SwpYn4dE}{\faLinkedin}\hspace{2mm}
\href{https://github.com/RheagalFire/Scalable-Hybrid-Rag}{\faGithub}\hspace{2mm}
\href{https://docs.google.com/presentation/d/1a6ENOwzwmHTZ1k66ErT51CDKL4EksXiEYehhHRsKwWU/edit?usp=sharing}{\faFilePowerpoint}
\end{itemize}

%===========================
\begin{flushleft}
\bf{\Large{Skills}}
\end{flushleft}
\vspace{-1mm}
\noindent\rule{\textwidth}{0.4pt}
\begin{itemize}
\setlength\itemsep{0.01em}
\item \textit{Languages:} Python, C++
\item \textit{Libraries:} Numpy, Pandas, Scikit, Tensorflow, Keras, Langgraph, Model Context Protocol, Unsloth
\item \textit{Frameworks:} Flask, Streamlit, FastAPI
\item \textit{Observability:} Langfuse, Arize Phoenix, Grafana, OpenTelemetry
\item \textit{Databases:} MySQL, MongoDB, Postgres, Qdrant, Redis
\item \textit{Cloud:} AWS, GCP, Azure, Terraform
\end{itemize}
%===========================
%===========================
\vspace{1mm}
\begin{flushleft}
\bf{\Large{Education}}
\end{flushleft}
\vspace{-2mm}
\noindent\rule{\textwidth}{0.4pt}
\vspace{2mm}

\noindent
\textbf{National Institute of Technology Raipur} \hfill \textbf{2023} \\
B.Tech \hfill \textbf{CPI: 8.59}
%===========================
\end{document}